$^{2}$H$(e,e'p)n$ Cross Section Measurements for Neutron Recoil Momenta up to $p_{r}\sim1.01$ GeV/c at $Q^{2}=4.5\pm0.5$ (GeV/c)$^{2}$

### 2020-03-07 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/body.tex
updated

simulation program, SIMC. Additional $^{1}\mathrm{H}(e,e'p)$ data were also taken at three other kinematic settings that covered the SHMS momentum acceptance range for the deuteron and were used for spectrometer optics optimization, 

@@

originated from the same reaction vertex at the target. See Supplemental Material \cite{Suppl_Mat} for details of the analysis cuts.\\

@@

and added in quadrature for overlapping $p_{r}$ bins. For $\theta_{nq}= 35^{\circ}, 45^{\circ}$ and $75^{\circ}$ (presented in this Letter) the overall kinematic uncertainty varied up to 6.5$\%$ for $p_{\mathrm{r}}\lesssim 1$ GeV/c.

@@

\indent The data were radiatively corrected for each bin in ($\theta_{nq}, p_{\mathrm{r}}$) by multiplying the measured cross sections by the ratio of the calculated particle yield excluding and including radiative effects. The Monte-Carlo code SIMC was used for these calculations with the Deuteron Model by J.M. Laget including FSI \cite{LAGET2005}.

@@

over the kinematic bin.\\

>>>>

simulation program, SIMC \cite{PhysRevC.64.054610}. Additional $^{1}\mathrm{H}(e,e'p)$ data were also taken at three other kinematic settings that covered the SHMS momentum acceptance range for the deuteron and were used for spectrometer optics optimization, 

@@

originated from the same reaction vertex at the target (See Supplemental Material \cite{Suppl_Mat}).\\

@@

and added in quadrature for overlapping $p_{r}$ bins. For $\theta_{nq}= 35^{\circ}, 45^{\circ}$ and $75^{\circ}$ (presented in this Letter) the overall kinematic uncertainty varied up to 6.5$\%$.

@@

\indent The data were radiatively corrected for each bin in ($\theta_{nq}, p_{\mathrm{r}}$) by multiplying the measured cross sections by the ratio of the calculated particle yield excluding and including radiative effects. The SIMC simulation code was used for these calculations with the Deuteron Model by J.M. Laget including FSI \cite{LAGET2005}.

@@

over the kinematic bin. The systematic uncertainty associated with the radiative and bin-centering corrections was investigated using the J.M. Laget PWIA and FSI models but negligible effects on the cross sections were found.\\
